A Neural Network Alternative to Convolutive Audio Models for Source Separation

### 2017-06-12 paper/paper.tex
Updated results section and figs

\begin{figure*}[t]
\centering
  \includegraphics[clip, trim = 3cm 2.4cm 3cm 2.1cm, width=\linewidth, height = 0.7\columnwidth]{Figs/Bases.eps}
  \caption{Decoder filters obtained by training the CAE on magnitude-spectrograms of utterances of a male speaker. This decomposition is obtained for the configuration $K = 80$ and $T = 8$. We see that the filters resemble snippets of a speech spectrogram.}~\label{fig:cnn_demo_speech}
\end{figure*}

@@

\begin{figure*}[ht!]
\centering
  \includegraphics[clip, trim = 0cm 0cm 0cm 0cm, width=0.95\linewidth]{Figs/CNN_Separation_Performance.png}
  \caption{Separation performance of convolutive models obtained using a CNN-CNN Auto-encoder for varying values of $K$. }~\label{fig:cnnseparation_performance}
\end{figure*}

@@

We see that the CAE models significantly out-perform their corresponding FF versions. This can be seen from the fact that the inter-quartile range in SDR for CAE models is higher than the inter-quartile range of corresponding FF models for several values of $K$. This improvement is a consequence of reduced interference generated by these models in source separation (See SIR plots). Although the SAR for CAE models degrades slightly as compared to FF models, the improvement in significant improvement in SIR compensates for this loss.

>>>>

\begin{figure}[ht!]
\centering
  \includegraphics[clip, trim = 0cm 0cm 0cm 0cm, width=\columnwidth, height = 0.8\columnwidth]{Figs/Bases.png}
  \caption{A subset of decoder filters obtained by training the CAE on magnitude-spectrograms of utterances of a male speaker. This decomposition is obtained for the configuration $K = 80$ and $T = 8$. We see that the filters resemble snippets of a speech spectrogram.}~\label{fig:cnn_demo_speech}
\end{figure}

@@

\begin{figure*}[ht!]
\centering
  \includegraphics[clip, trim = 0cm 0cm 0cm 0cm, width=\linewidth]{Figs/FullPerformance.png}
  \caption{Separation performance of convolutive models obtained using a CNN-CNN Auto-encoder for varying values of $K$. }~\label{fig:cnnseparation_performance}
\end{figure*}

@@

We see that the CAE models significantly out-perform their corresponding FF versions. This can be seen from the fact that the inter-quartile range in SDR for CAE models is higher than the inter-quartile range of corresponding FF models for several values of $K$. This improvement is a consequence of reduced interference generated by these models in source separation (See SIR plots). Although the SAR for CAE models degrades slightly as compared to FF models, the improvement in significant improvement in SIR compensates for this loss. The performance of the models achieves a peak value for $K=80$. However, the separation performance does not degrade significantly for other values of $K$. Thus, the choice of $K$ does not appear to be a very critical consideration for these models.

The convolutive speech models obtained by training the RCAE also outperform the FF auto-encoder models, as seen by the median values and inter-quartile ranges. This improvement in performance is not as pronounced as the CAE models for the case of speech mixtures. However, the experimentation serves as a proof of concept that exploring non-uniform auto-encoder architectures could lead to interesting and potentially powerful algorithms for several applications.
